Stochastic Newton with Arbitrary Sampling

### 2023-02-25 paper/main.tex
updated abstract

	The problem of minimizing the average of a large number sufficiently smooth and strongly convex functions is ubiquitous in machine learning. Stochastic first-order methods for this problem of Stochastic Gradient Descent type are well studied. In turn, second-order methods, such as Newton, have certain advances since they can adapt to the curvature of the problem. They are also known for their fast convergence rates. But stochastic variants Newton-type methods are not well-studied and have limitations on the batch size. Dmitry Kovalev et al proposed a method which requires no limitations on batch sizes. Our goal is to explore this method with different sampling strategies that lead to practical improvements.

@@

\keywords{}

>>>>

	The problem of minimizing the average of a large number of sufficiently smooth and strongly convex functions is ubiquitous in machine learning. Stochastic first-order methods for this problem of Stochastic Gradient Descent type are well studied. In turn, second-order methods, such as Newton, have certain advances since they can adapt to the curvature of the problem. They are also known for their fast convergence rates. But stochastic variants of Newton-type methods are not studied as good as SGD-type ones and have limitations on the batch size. Dmitry Kovalev et al proposed a method which requires no limitations on batch sizes. Our goal is to explore this method with different sampling strategies that lead to practical improvements.

@@

\keywords{Stochastic Newton, sampling strategy}
